\documentclass[11pt]{article}
\usepackage{setspace}
\setstretch{1}
\usepackage{amsmath,amssymb, amsthm}
\usepackage{graphicx}
\usepackage{bm}
\usepackage[hang, flushmargin]{footmisc}
\usepackage[colorlinks=true]{hyperref}
\usepackage[nameinlink]{cleveref}
\usepackage{footnotebackref}
\usepackage{url}
\usepackage{listings}
\usepackage[most]{tcolorbox}
\usepackage{inconsolata}
\usepackage[papersize={8.5in,11in}, margin=1in]{geometry}
\usepackage{float}
\usepackage{caption}
\usepackage{esint}
\usepackage{url}
\usepackage{enumitem}
\usepackage{subfig}
\usepackage{wasysym}
\newcommand{\ilc}{\texttt}
\usepackage{etoolbox}
\usepackage{algorithm}
\usepackage{changepage}
% \usepackage{algorithmic}
\usepackage[noend]{algpseudocode}
\usepackage{tikz}
\usetikzlibrary{matrix,positioning,arrows.meta,arrows}
\patchcmd{\thebibliography}{\section*{\refname}}{}{}{}
% \PassOptionsToPackage{hyphens}{url}\usepackage{hyperref}

\providecommand{\myceil}[1]{\left \lceil #1 \right \rceil }
\providecommand{\myfloor}[1]{\left \lfloor #1 \right \rfloor }


\begin{document}



\title{\textbf{CSDS 455: Homework 6}}

\author{Shaochen (Henry) ZHONG, \ilc{sxz517}}
\date{Due and submitted on 09/14/2020 \\ Fall 2020, Dr. Connamacher}
\maketitle

\section*{Problem 1}

\begin{proof}
We have $rad(G) \leq diam(G)$ proven by definition. Now locate vertices $u, v \in V(G)$ with $diam(G) = d(u, v)$, then locate a vertex $c$ to the center of $G$. We know that $diam(G) = d(u, v) \leq d(u, c) + d(c, v) \leq 2\epsilon(c)$. Due to the nature of $c$ being a center vertex, we also know that any vertex has a $\epsilon(c) = rad(G)$ by definition, thus we have $diam(G) \leq 2rad(G)$ and the statement is proven by direct proof.
\end{proof}

\section*{Problem 2}

\begin{proof}

The question is essentially same as proving that the Prim's algorithm produced tree $P$ is a minimum weight spanning tree of $G$. This is because if $T$ is a minimum weight spanning tree of $G$ with a weight of $W$, by doing the equal-weight-edge-replacements on $T$ to make $T', T'', T'''$... we will eventually have a replaced version of $T$ that is same as $P$, as both $T$ and $P$ (if being a minimum weight spanning tree of $G$) have a weight of $W$.

\leavevmode\newline


    \begin{adjustwidth}{1cm}{}

    \textbf{Lemma (Cut Property): Assume $S \in V(G)$ with $G$ being a graph with distinct edge weights. If the minimum cost edge between $V-S$ and $S$ is $e$, this edge $e$ must be contained in the minimum weight spanning tree of $G$}.\newline
    \begin{proof}
    To prove by contradiction: Denote the minimum weight spanning tree of $G$ to be $M$ and assume edge $e$ is not in it. This means there must be some other edge $e'$ that connects $V$ to $V-S$. Since we know that $w(e) < w(e')$ and $M$ is connected, $M - e' + e'$ will another spanning tree of $G$ and has a lower weight. This contradicts the assumption of $M$ being a minimum weight spanning tree of $G$, and the statement is therefore proven.
    \end{proof}
    \end{adjustwidth}

With the lemma proven. Now assume $P$ is not a minimum weight spanning tree of $G$ and traverse through the sequences of vertices of $P$ and $T$. Let $P_{k+1} \subseteq P$ denotes the first tree that has an edge that is not contained in $T$ (as in $P$, it went from its $k$-th vertex $x$ to $(k+1)$-th vertex $y$; but in $T$, it went from its $k$-th vertex $x$ to $(k+1)$-th vertex $z$). \newline

Now we denotes $P_k = P_{k+1} - y$, and edge $<x, y>$ to be the minimum edge from $P_k$ to $V - P_k$ (as it is defined by the mechanism of Prim's algorithm). By lemma, this edge $<x, y>$ must be in the minimum weight spanning tree $T$. However, $<x, y>$ is not in $T$ as $T$ should chose edge $<x, z>$. This contradicts the setting and our assumption of $P$ is not a minimum weight spanning tree of $G$ is therefore voided.

Since at the beginning we have estalished that proving $P$ to be a minimum weight spanning tree of $G$ is equivalent to the proposed statement. The statment is therefore proven.\newline

Note the lemma is proved based on the assumption of a graph having distinct edge weights. However, this may not be true for the proposed $G$. Which would suggest a minimal cost edge $e$ may not been chosen to connect $V$ to $V-S$ as an alternative edge $e''$ with $w(e'') = w(e)$ is chosen. However, this won't effect the conclusion as as long as $P$ has the same weight of a minimum weight spanning tree, we may convert $T$ to $P$ by doing the equal-weight-edge-replacement manuver.

\end{proof}

\section*{Problem 3}



\section*{Problem 4}



% \section{References}
%
% \nocite{*}
% \raggedright
% \bibliography{references.bib}
% \bibliographystyle{plain}


\end{document}