\documentclass[11pt]{article}
\usepackage{setspace}
\setstretch{1}
\usepackage{amsmath,amssymb, amsthm}
\usepackage{graphicx}
\usepackage{bm}
\usepackage[hang, flushmargin]{footmisc}
\usepackage[colorlinks=true]{hyperref}
\usepackage[nameinlink]{cleveref}
\usepackage{footnotebackref}
\usepackage{url}
\usepackage{listings}
\usepackage[most]{tcolorbox}
\usepackage{inconsolata}
\usepackage[papersize={8.5in,11in}, margin=1in]{geometry}
\usepackage{float}
\usepackage{caption}
\usepackage{esint}
\usepackage{url}
\usepackage{enumitem}
\usepackage{subfig}
\usepackage{wasysym}
\newcommand{\ilc}{\texttt}
\usepackage{etoolbox}
\usepackage{algorithm}
\usepackage{changepage}
% \usepackage{algorithmic}
\usepackage[noend]{algpseudocode}
\usepackage{tikz}
\usetikzlibrary{matrix,positioning,arrows.meta,arrows}
\patchcmd{\thebibliography}{\section*{\refname}}{}{}{}
% \PassOptionsToPackage{hyphens}{url}\usepackage{hyperref}

\providecommand{\myceil}[1]{\left \lceil #1 \right \rceil }
\providecommand{\myfloor}[1]{\left \lfloor #1 \right \rfloor }


\begin{document}



\title{\textbf{CSDS 455: Homework 11}}

\author{Shaochen (Henry) ZHONG, \ilc{sxz517}}
\date{Due and submitted on 09/30/2020 \\ Fall 2020, Dr. Connamacher}
\maketitle

\textit{I have discussed with Yuhui Zhang and Yige Sun for this assignment.} Also sorry if this one is a bit ``sloppy'' -- have to watch the debate!

\section*{Problem 1}

We have the total charge of a graph being $C = C_v + C_f$, know that $\sum_{f \in F}|f| = \sum_{v \in V} d(v) = 2|E|$ and by Euler's formular $|V| - |E| + |F| = 2$we have:

\begin{align*}
    C &= \sum_{v \in V}(d(v) - 4) + \sum_{f \in F}(|f| - 4) \\
    &= 2|E| - 4|V| + 2|E| - 4|F| \\
    &= 4|E| - 4|V| - 4|F| \\
    &= 4(|F| - 2) - 4|F| \\
    &= -8 < 0
\end{align*}

Thus, the total charge is negative.





\section*{Problem 2}

A $v$ with $d(v) = 3$ will have a charge of $-1$, and by requirement it will be one three faces with size 6 or larger. This suggests if we need to ``discharge'' this $v$, each face will get $-\frac{1}{3}$ negative charge upon it from this $v$.

For a face $f$, assume all of its vertices are 3-degree and have a $-1$ charge, then the total charge of this face will be $\frac{|f|}{3} + |f| - 4$. By observation we may tell as long as $|f| \geq 6$, such equation is $\geq 0$. Combined with the fact that all the negative charges of on-face vertices are now ``discharged'', the ``every vertex of $G$ and every face of $G$ of size 6 or larger has non-negative charge'' requirement is now statsfied. Also because we simply added the negative charge of a 3-degree vertex onto a 6-size-or-greater face it is on, the total charge of $G$ will be unaffected.

\section*{Problem 3}

\begin{proof}
    To proof by contradiction. Assume that every vertex in $G$ on face $f$ has $d(v) + |f| > 8$, which suggests for every vertex $v$ on face $f$, there is $d(v) - 4 + |f| - 4 > 0$. For $\delta(G) \geq 3$, this suggests for a 3-degree vertex $v$, its neighbored face $f$ must be $|f| \geq 6$ to statsfies the pervious inequality.

    Now we may utilized the discharging rule introduced in \textit{Problem 2}. Which will make every vertex and faces of $G$ having a non-negative charge (as every vertex is neighbored with faces with $|f| \geq 6$), thus lead to a $G$ with a total non-negative charge. This is a contradiction to \textit{Problem 1} conclustion and the statement is therefore proved by contradiction.
\end{proof}

% \section{References}
%
% \nocite{*}
% \raggedright
% \bibliography{references.bib}
% \bibliographystyle{plain}


\end{document}