\documentclass[11pt]{article}
\usepackage{setspace}
\setstretch{1}
\usepackage{amsmath,amssymb, amsthm}
\usepackage{graphicx}
\usepackage{bm}
\usepackage[hang, flushmargin]{footmisc}
\usepackage[colorlinks=true]{hyperref}
\usepackage[nameinlink]{cleveref}
\usepackage{footnotebackref}
\usepackage{url}
\usepackage{listings}
\usepackage[most]{tcolorbox}
\usepackage{inconsolata}
\usepackage[papersize={8.5in,11in}, margin=1in]{geometry}
\usepackage{float}
\usepackage{caption}
\usepackage{esint}
\usepackage{url}
\usepackage{enumitem}
\usepackage{subfig}
\usepackage{wasysym}
\newcommand{\ilc}{\texttt}
\usepackage{etoolbox}
\usepackage{algorithm}
% \usepackage{algorithmic}
\usepackage[noend]{algpseudocode}
\usepackage{tikz}
\usetikzlibrary{matrix,positioning,arrows.meta,arrows}
\patchcmd{\thebibliography}{\section*{\refname}}{}{}{}


\begin{document}



\title{\textbf{CSDS 455: Homework 2}}

\author{Shaochen (Henry) ZHONG, \ilc{sxz517}}
\date{Due and submitted on 08/31/2020 \\ CSDS 455, Dr. Connamacher}
\maketitle

\section{Problem 1}

If the algorithm perform the \ilc{BFS} in the following way, it is possible to achieve the demonstrated \textit{maximal matching} during middle of the iteration process.

For the ease of description, let's label the nodes from left set ($U$) of the bipartite graph $A, B, C, D, E, F$ from top to bottom; and label the nodes from right set ($V$) of the the bipartite graph as $(1), (2), (3), (4), (5)$ from top to bottom. And we have a empty list $M$.

\begin{itemize}
    \item Find a unchecked node $\in U$ labelled with biggest alphabetical value, let the node be $\alpha$
    \item Gather all child nodes of $\alpha$ $\in V$ into a list $\beta$, then sort $\beta$ decendingly based on each node's degree (number of edges connected). If two nodes have the same degree, the node with lower numerical value will store prior in the list.
    \item Pop the first node from $\beta$ to check until $\beta$ is empty.
    \item Find a unchecked node $\in U$ labelled with biggest alphabetical value and repeat the whole list.
\end{itemize}

Here's a emulation of a \textsc{Hopcroft-Karp} algorithm implemented with the above \ilc{BFS}.

\begin{itemize}
    \item The unchecked node with largest alphabetical value $\in U$ is node $F$.
    \item The child nodes of $F$ $\in V$ are $\{(1), (4)\}$. With $\delta{(1)} = 1$ and $\delta{(4)} = 3$. Therefore edge $<F, (4)>$ is checked. Since it is a single edge argumenting path, it is added to $M$.
    \item The unchecked node with largest alphabetical value $\in U$ is node $E$.
    \item The child nodes of $E$ $\in V$ are $\{(3), (5)\}$. With $\delta{(3)} = 3$ and $\delta{(4)} = 5$. Since node $(3)$ has a lower numerical value, edge $<E, (3)>$ is checked. Since it is a single edge argumenting path, it is added to $M$.
    \item The unchecked node with largest alphabetical value $\in U$ is node $D$.
    \item The child nodes of $D$ $\in V$ are $\{(2), (5)\}$. With $\delta{(2)} = 1$ and $\delta{(5)} = 3$. Therefore edge $<D, (5)>$ is checked. Since it is a single edge argumenting path, it is added to $M$.
\end{itemize}

The given \textit{maximal matching} is obtained through the above iteration of \textsc{Hopcroft-Karp} algorithm. The statement is proven by direct example.

\section{Problem 2}

This problem will inherit the labeling and list $M$ introduced by the above problem.

For $C, B, A \in U$, all of their child nodes $\in V$ are not free. Thus, we will check for the free nodes $\in U$ for non-single-edged \textit{argumenting paths}.\newline

Starting with node $C$, as it has the largest alphabetical value of all free nodes $\in U$. It has two child nodes $\in V$, $\{(4), (5)\}$, both having a degree of $3$. Thus we first check node $(4)$ since it has a lower numerical value. Since we are looking for an \textit{argumenting paths}, the only node we can proceed from $(4)$ is $F$, as it is the only \textit{matching edge} connected to $(4)$. The only node we can proceed from $F$ is $(1)$, as it is the only free node conncted to $F$.

Now, with DFS from $(1)$, we have discovered an \textit{argumenting paths} of $<C, (4), F, (1)>$. Thus, we remove the \textit{matching edge} $<(4), F>$ from $M$, then add edge $<C, (4)>$ and $<F, (1)>$ to $M$.\newline

Since there will be no more \textit{argumenting paths} in the graph (as we can't find any more alternating path which starts and ends on free nodes). This $\{ <F, (1)>, <E, (3)>, <D, (5)>, <C, (4)> \}$, with a cardinality of $4$, be the \textit{maximum matching} for the graph.

\section{Problem 3}

Imaging a subgraph $F$ of $G$, which is consisted by and only by edges in $M \sqcup N$ (edges that only $\in M$ or only $\in N$). Since $|M| > |N|$, we know that there must be $M \cap F > N \cap F$. Also for the ease of description, we initialize $M' = M$ and $N' = N$.

We also know that every node in $F$ will either have degree of $1$, where such node belongs and only belongs to $M$ or $N$; or degree of $2$, where such node is connected to an edge in $M$, and also conncted to an edge in $N$. \newline


We first inspect edges in $F$. If there is an edge $E \in M$ from $F$ that is a single edge (connected between two degree $1$ nodes), we remove it from $M'$ and add it to $N'$. This will make $|M'| = |M| - 1$ and $|N'| = N + 1$. We may tell that the new $M'$ and $N'$ are still matchings of $G$, due to the fact that for a single edge $\in M \sqcup N$, its two nodes are not connected to any edge of $M \cap N$, thus we won't have two edges of $N'$ sharing a node of $E$.\newline



If there is no single $E \in M$ from $F$, since $M \cap F > N \cap F$, there must be an alternating path $P$ in $F$ which starts and ends on edges of $M$. We inspect edges on this path: if an edge $EP \in P$ is also in $M$, we remove it from $M'$ and add it to $N'$; vice versa, if an edge $EP \in P$ is also in $N$, we remove it from $N'$ and add it to $M'$. Namely, we swapped the attribution of edges in $P$.

This maneuver will make $|M'| = |M| - 1$ and $|N'| = N + 1$, since path $P$ starts and ends on edges of $M$, there must be one more $M$ edge in $P$ than $N$ edges. Also the new $M'$ and $N'$ are still matchings of $G$, as the start- and end-nodes of path $P$ are not connecting to any edges from $M \cap N$.\newline


In both cases, we will have $M \cup N = M' \cup N'$ and $M \cap N = M' \cap N'$. Since we only swapped edge(s) in $M \sqcup N$ -- which won't effect the intersection and union the two matchings.\newline





% \section{References}
%
% \nocite{*}
% \raggedright
% \bibliography{references.bib}
% \bibliographystyle{plain}


\end{document}